Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-03-19 ms.tex
I started a summary table of all observations.

The Kepler spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
During this time, the transit depths averaged around (??0.55\%) but varied stochastically from just one 15.7 hour orbit to the next.
\citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month.

@@

\begin{deluxetable*}{lr}
\tablecaption{List of observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date} & Comment \\
UT & \\
 }
\startdata
UT 2016-06-10 & Clouds \\
UT 2016-06-12 & Good \\
UT 2016-06-14 & Good \\
UT 2016-07-12 & Good \\
UT 2016-07-14 & Good \\
UT 2016-07-16 & Good \\
\enddata
\tablenotetext{}{Obs Summary.}
\end{deluxetable*}

>>>>

The Kepler spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
During this time, the transit depths averaged around $\sim$0.6\% but varied stochastically from just one 15.7 hour orbit to the next.
\citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month.

@@

\begin{deluxetable*}{lr}
\tablecaption{List of observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
 }
\startdata
2016-06-10 & Clouds \\
2016-06-12 & Good \\
2016-06-14 & Good \\
2016-07-12 & Good \\
2016-07-14 & Good \\
2016-07-16 & Good \\
\enddata
\tablenotetext{}{Summary of observations in this work.}
\end{deluxetable*}

\section{Previous Observations}

\begin{deluxetable*}{lrrrr}
\tablecaption{List of published observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date Start} &
\colhead{Date End} &
\colhead{Observatory} &
\colhead{Filter} &
\colhead{Reference(s)} \\
UT & UT & & & \\
 }
\startdata
2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
2013-08-13 & 2013-09-03 & IRTF & $g'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2014-08-14 & 2013-09-04 & IRTF & $g'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
\enddata
\tablenotetext{}{Summary of published observations of \sha.}
\end{deluxetable*}
